---
title: "'Is the prognostic value of primary tumor location in patients with KRAS and wild-type mutation different?: a meta-analysis"
  metastatic  colorectal cancer: a meta-analysis'
author: "Michail Belias"
date: "05/11/2019"
output: pdf_document
---

```{r}

# right vs. left colon



Wild.Type.dataset = data.frame(
Authors = c("20050181 (Panitumumab + FOLFIRI)","20050181 (Folfiri)",
            "20020408 (Panitumumab + BSC)","20020408 (BSC)",
            "von Einem","Loupakis",
            "Taieb (Double WT)"),
"Study design" =c("RCT","RCT","RCT","RCT","Cohort study","Observational","RCT"),
`Treament`     =c("Panitumumab + FOLFIRI","FOLFIRI","Panitumumab + BSC","BSC","Cetuximab +  CAPIRI or CAPOX","?","Cetuximab with or Without FOLFOX"),


`Wild type Effect size`=         c(2.01,   1.51,   1.89,   2.41,   2.38,   NA,   1.62),
`Wild type Lower_CI` =           c(1.29,   0.96,   0.95,   1.21,   1.49,   NA,   1.08),
`Wild type Upper_CI` =           c(3.13,   2.37,   3.76,   4.81,   4.00,   NA,   2.41),
`Wild type Number of patients` = c(181,    187,    58,     57,     95,     NA,   715), 
Year =                           c(2014,   2014,   2014,   2014,   2014,   2018, 2017),

check.names = FALSE)

#

RAS.mutated.df = data.frame(
Authors = c("PRIME(Panitumumab + FOLFOX)","PRIME(FOLFOX)",
            "PEAK(Panitumumab + FOLFOX)","PEAK(Bevacizumab + FOLFOX)",
            "20050181 (Panitumumab + FOLFIRI)","20050181 (FOLFIRI)",
            "20020408 (Panitumumab + BSC)","20020408 (BSC)",
            "von Einem",
            "Loupakis Cod12","Loupakis Cod13","Loupakis (others)","Loupakis NRAS",
            "Taieb (RAS mutated)","Taieb (BRAF mutated)"),
"Study design" =c("RCT","RCT","RCT","RCT","RCT","RCT","RCT","RCT","Cohort study","Observational","Observational","Observational","Observational","RCT","RCT"),
`Treament`     =c("Panitumumab + FOLFOX","FOLFOX","Panitumumab + FOLFOX","Bevacizumab + FOLFOX",
                  "Panitumumab + FOLFIRI","FOLFIRI","Panitumumab + BSC","BSC",
                  "Cetuximab +  CAPIRI or CAPOX","?","?","?","?","Cetuximab with or Without FOLFOX","Cetuximab with or Without FOLFOX"),
`KRAS Effect size`=         c(1.17,   1.09,   2.24,   2.8,   0.84,   1.46,   1.26,   1.6,   0.77,   1.07,   0.68,   0.76,   0.84,   1.01,   0.84),
`KRAS Lower_CI` =           c(0.85,   0.87,   0.87,   1.05,  0.63,   1.09,   0.67,   0.95,  0.43,  0.77,   0.32,   0.32,   0.27,   0.77,   0.46),
`KRAS Upper_CI` =           c(1.61,   1.48,   5.78,   7.43,  1.11,   1.96,   2.36,   2.68,  1.47,  1.48,   1.43,   1.80,   2.65,   1.33,   1.55),
`Kras Number of patients` = c(230,    228,    25,     29,    259,    260,    77,     98,    68,    340,    86,     56  ,     36,   942 ,   212 ),  


check.names = FALSE)




Median.Survival.To.HR = function(x) {(log(2) / x)}



```




## Background
The prognostic value of primary tumor location (PTL) in patients with metastatic colorectal cancer has been investigated over the years and seems to be clear and consistent. However, recent studies indicate that this prognostic ability may vary in patients with KRAS and wild-type mutation. 

## Objective 
Our goal is to summarise the evidence and assess the prognostic value of PTL in patients with metastatic colorectal cancer stratified by KRAS mutational status. 

## Methods
We searched the literature to identify studies that compare the assocation PLT and overall survival in patients with KRAS and wild-type mutations. 

## Study selection
Our eligibility criteria were: 

* Year of publication
* Design of study (RCTs, Observational, ....)?
* Definition of left right tumour?
* Survival outcome was reported 
* Written in English ??


## Results
A total of xxx potentially relevant studies were reviewed. After screening the abstracts and excluding duplicates, we ended up with xx studies. After taking into consideration the full text ended up 5 studies published from xxxx to xxxx were analysed. The total number of patients was xxxx. Per study number of patients ranged from xx to xx (median)

## Conclustions



```{r}
library(meta)

### log-transform hazard ratios and compute standard error based on the
Wild.Type.logyi  <- log(Wild.Type.dataset$`Wild type Effect size`) 
Wild.Type.sei <- with(Wild.Type.dataset, log(`Wild type Upper_CI`) - log(`Wild type Lower_CI`)) / (2*1.96)
Wild.Type.res <- metagen(TE = Wild.Type.logyi, seTE =Wild.Type.sei,
                         studlab = Wild.Type.dataset$Authors,comb.fixed = T,comb.random = T,hakn = T,method.tau = "EB" ) 

forest(Wild.Type.res, prediction = T)


### log-transform hazard ratios and compute standard error based on the
RAS.mutated.logyi  <- log(RAS.mutated.df$`KRAS Effect size`) 
RAS.mutated.sei <- with(RAS.mutated.df, log(`KRAS Upper_CI`) - log(`KRAS Lower_CI`)) / (2*1.96)
RAS.mutated.res <- metagen(TE = RAS.mutated.logyi, seTE =RAS.mutated.sei,
                           studlab = RAS.mutated.df$Authors,comb.fixed = T,comb.random = T,hakn = T,method.tau = "EB" ) 

forest(RAS.mutated.res, prediction = T)

```





